{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-09-26 thesis/overview.tex
finish glossing

\subsection{Concurrency Primitives}

@@

\subsection{The state space}

@@

		A program behaviour which manifests nondeterministically depending on the thread scheduling pattern,

@@

	\item {\bf DPOR.} See {\em dynamic partial order reduction}.

@@

		% TODO

@@

		% TODO

@@

@@

		% TODO

@@

		The act of making a {\em state space} smaller by finding multiple execution sequences that can be proved equivalent,

@@

		Concurrency testing {\em dynamic analysis} technique involving controlling a system's nondeterminism
		to exhaustively check all possible thread interleavings.

@@

		% TODO

@@

	\item {\bf TA.} See {\em teaching assistant}.

@@

		characterized by the two different program states at beginning and end.

>>>>

\subsection{Concurrency primitives}
\label{sec:overview-mutex}

@@

\subsection{The state space}
\label{sec:overview-statespace}

@@

		A program behaviour which manifests {\em nondeterministically} depending on the thread scheduling pattern,

@@

	\item {\bf DPOR.} {\em Dynamic partial order reduction}.

@@

		Representation of the {\em state space} by joining interleavings with common prefixes
		into a subtree with a branch at each point they diverge, forming a tree overall.
		See \sect{\ref{sec:overview-statespace}}; Figure~\ref{fig:tree}.

@@

		A data structure used to ensure {\em atomic} access to shared state
		with respect to other {\em threads} using the same lock.
		See \sect{\ref{sec:overview-mutex}}.

@@

	\item {\bf Nondeterminism.}
		Property of a program which can exhibit different behaviours across multiple runs,
		despite no change in the input data.

@@

		A test of an intermediate execution state returning whether the {\em model checker}
		should inject {\em preemptions} to force another thread to interleave.
		Often simply ``is it the beginning of {\tt mutex\_lock()} or {\tt mutex\_unlock()}?'',
		but may be extended to include the program counter values of known {\em data races},
		or to further restrict by predicates on the current stack trace.
		See \sect{\ref{sec:landslide-pps}}.
		Often called {\em preemption point} for short, with context hopefully making the distinction clear.

@@

		The act of making a {\em state space} smaller by finding multiple execution sequences
		that can be proved {\em equivalent},

@@

		Concurrency testing {\em dynamic analysis} technique involving controlling a system's {\em nondeterminism}
		to exhaustively check all possible {\em thread interleavings}.

@@

		The set of all possible behaviours of a program under any interleaving of threads.
		As opposed to modern {\em stateless model checkers}, older MCs stored the set of states explicitly,
		attempting to cover them by traversing as few edges (executing as few {\em transitions}) as possible;
		hence the name.
		Modern MCs instead cover these states implicitly by instead exhaustively executing all {\em interleavings},
		using {\em DPOR} to prune redundant {\em equivalent} ones which could only revisit old states.
		The slightly misleading name is kept for consistency with prior work (sorry).

@@

	\item {\bf TA.} {\em Teaching assistant}.

@@

		bounded by the two different program states at beginning and end.
